Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-10-25 paper/paper.qmd
Add files via upload

model_date <-
  readRDS(file = here::here("models/model_date.rds"))
model_date_pollster <-
  readRDS(file = here::here("models/model_date_pollster.rds"))
```

@@

modelsummary(models = list("Model with date" = model_date, 
                           "Model with date and pollster" = model_date_pollster),
             statistic = "conf.int",
             conf_level = 0.95,
             stars = TRUE,
             coef_rename = coef_names,
             output = "kableExtra") %>%
  kable_styling(full_width = F, position = "left", bootstrap_options = c("striped", "hover"
                                                                           , line_height = 0.8)) %>%
  column_spec(column = 2, width = "2em") %>%
  column_spec(column = 2, width = "4em") %>%
  add_header_above(c(" " = 1, "Model Summary" = 2)) %>%
  kable_classic(full_width = F, font_size = 6) %>%
  add_footnote("This table shows the regression models with custom variable names.")

>>>>

model_final_glm <-
  readRDS(file = here::here("models/model_final.rds"))
model_bayes <-
  readRDS(file = here::here("models/model_bayes.rds"))
```

@@

modelsummary(models = list("Model by glm" = model_final_glm, 
                           "Model by bayes" = model_bayes),
             statistic = "conf.int",
             conf_level = 0.95,
             stars = TRUE,
             coef_rename = coef_names,
             output = "kableExtra") %>%
  kable_styling(full_width = F, position = "left", bootstrap_options = c("striped", "hover"
                                                                           , line_height = 6)) %>%
  column_spec(column = 2, width = "2em") %>%
  column_spec(column = 2, width = "4em") %>%
  add_header_above(c(" " = 1, "Model Summary" = 2)) %>%
  kable_classic(full_width = F, font_size = 4) %>%
  add_footnote("This table shows the regression models with custom variable names.")
